Untitled

### 2021-03-14 analysis/chapters/paper_ana_20181122.Rmd
Tabla radianzas

>>>>

```{r}
fread(here("analysis", "data", "derived_data", "tabla_radianzas.csv")) %>% 
  .[, ":="(sensor = toupper(sensor),
           plataforma = toupper(plataforma),
           prop = scales::percent(prop/100, accuracy = 0.01, trim = TRUE))] %>% 
  .[order(.[,'sensor']), ] %>% 
  .[] %>% 
  kbl(col.names = c("Sensor", "Plataform", "Number of assimilated\nchannels", "Percentage over total"),
      caption = "List of the available sensors in several platforms, the number of accepted channels and the percentage of assimilated observations calculated over all radiance observations.") %>% 
  collapse_rows(1) %>% 
  kable_classic_2(full_width = F)
```
